Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-01 paper/main.tex
revision of Methodes until COPEs

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English). The categorie
    \texttt{++} also contains adverbial adjectives and adverbs}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable objects insides and outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundarie & telephone, car \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\todo[inline]{as usually I am pretty unsure about correct report of motion
correction \& template creation}
\todo[inline]{Satz zum Downsampling der 7T Daten? => check github repo}
% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series data were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data are already aligned to a subject-specific
\href{https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}{3
Tesla BOLD template} by a rigid body transformation in MCFLIRT
\citep{jenkinson2002registration} to correct for motion during scanning
\citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant was dropped to due to invalid distortion correction
during scanning of the AO stimulus

% preprocessing intro
All further analysis steps in the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
Library}; \citep{smith2004fsl} on a computer cluster running the
\href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% actual preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency \citep{woolrich2001autocorr}.

@@

For both naturalistic stimli, we conducted a standard two-level general linear
model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
across the 8 segments for every subject. A subsequent, third-level analysis averaged contrast estimates over subjects.

@@

\todo[inline]{Nouns, die eigentlich zu einer anderen Kateogrie als setting\_new
    or setting\_old gehören, aber einen Settingwechsel anzeigen, werden als
Event eines der Settingwechsel zugehörig gezählt.}

At the first level analyzing each segment for every subject, we created
regressors for the AO data from the narrator's descriptive nouns (see Table
\ref{tab:descr-nouns-counts}) added to the annotation of speech
\citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from
events provided by an annotation of movie cuts and depicted locations
\citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
First, both annotations were split into eight parts corresponding to the eight
segments used as stimuli during fMRI scanning.

% AO events
To create regressors for the AO analysis, XY from the XY original categories
were selected [+++why?+++]. Some categories were pooled / joined / merged
resulting in 11 new categories to provide more events per category per run.
% categories taken from movie cut annotation
Five categories were created from the annotation of movie cuts to capture
variance of a change in soundscape after cuts and tu create contrasts of
cross-modal negative control.
% nuissance regressors
Two regressors reflecting auditory (low-level) features (left-right difference
in volume and root mean squared volume) aligned to the frame rate of
(\unit[40]{ms}) were modeled to reduce nuisance effects.
% siehe Tabelle
An overview and short explanation of the 11 speech-related and 5 movie
cut-related categories and the two low-level auditory features ca be found in
Table \ref{tab:ao-events}.

@@

\caption{Overview of events to build the 18 regressors for the analysis of the audio-only (AO) stimulus. Some of the original categories (female, females, fname; male, males, mname; face, head; object, objects; see Table \ref{tab:descr-nouns}) were pooled into new categories (sex\_f; sex\_m; fahead; object).

@@

For description of control condition for movie cuts see Table \ref{tab:av-events}}

@@

furn & big inventory of rooms (insides/outsides) & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline

@@

fg\_ad\_rms & root mean square loudness & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts in the movie into five categories:
1) unfamiliar setting (\texttt{vs\_new}),
2) familiar setting (\texttt{vs\_old}),
3) locale switch (\texttt{vlo\_ch}),
4) unfamiliar perspective (\texttt{vpe\_new}), and
5) familiar perspective (\texttt{vpe\_old}).
% no cut condition
A sixth regressors (\texttt{no\_cut}) was created to build negative control
contrasts.
\todo{how no\_cut condition was done; compare no\_speech oben und Masterarbeit}
% how it was done
Frames within a longer lasting were pseudo-randomly chosen by the following
rationale:
% siehe Tabelle
An overview and short explanation of these six regressors and six additional
event categories were of low-level auditory visual features of the movie can be
found in Table \ref{tab:av-events}.

\begin{table*}[t]
    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
\texttt{fg\_av\_ger\_lr} (left-right difference in ??? of consecutive movie frame).
\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
\texttt{fg\_av\_ger\_ud} (up-down difference in ??? of consecutive movie frames).
\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For description of control condition for movie cuts see Table \ref{tab:ao-events}}
\label{tab:av-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & XYZ & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & XYZ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & XYZ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & XYZ & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & XYZ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
\end{tabular}
\end{table*}

% modeling of regressors from events
For both stimuli, regressors created from nouns were modeled as boxcar functions
from the beginning to the end of noun.  Regressors created from movie cuts were
modeled as boxcar function lasting \unit[200]{ms} after a cut. Finally,
regressors created from low-level percetual features were modeled as box car
function from the beginning to the end of the corresponding movie frame lasting
\unit[40]{ms}. All regressors were convolved with a double gamma canonical
hemodynamic response function (HRF). Their temporal derivatives were added to
compensate for small timing differences \citep{friston1998event}.
% motion parameters
Six motion parameters were used as additional nuisance regressors.
% null regressors
If a segment did not contain a single event for a specific regressor, a null
regressor was chosen for that segment.
\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
einem ihren Videos mal gesagt} Finally, designs were filtered with the same
% high-pass filtering
high-pass filter (cutoff period of \unit[150]{s}) as the BOLD time series.
% siehe Tabelle für Correlation of regressors
\todo[inline]{hier kommt die Abbildung ``correlation of regressors''; ref to
fig:reg-corr}

\todo[inline]{in der Abbildung der Regressoren-Korrelationen sind jetzt alle
    Regressoren drin; imo könnte man ein paar herausnehmen (die zur Kontrolle
    benutzen Filmschnitt-Regressoren in der AO-Analyse, die zur Kontrolle
    benutzen Descriptive-Nouns Regressoren (namentlich se\_new und se\_old), und ggf. [ein paar der] low-level features nuissance regressors.}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}). Regressors were convolved with FSL's
        ``Double-Gamma HRF'' as a model of the hemodynamic response function,
        temporally filtered with the same high-pass filter (cut-off
        \unit[150]{s}) as the BOLD time series, and concatenated across runs
    before performing the correlation.}
    \label{fig:reg-corr}
\end{figure*}

>>>>

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English). The categorie
    \texttt{++} also contains adverbial adjectives and adverbs}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\todo[inline]{I revised part of motion correction/co-registration but as usually
I am pretty unsure about correctness}
\todo[inline]{Satz zum Downsampling der 7T Daten?}.

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants that took part in all three
experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHubi}.
Data were already corrected for motion and aligned by non-linear warping to a
particpant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.

% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software
Library}; \citep{smith2004fsl} on a computer cluster running the
\href{https://www.debian.org}{Debian} GNU/Linux operating system. Software
packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% actual preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

@@

For both naturalistic stimuli, we conducted a standard two-level general linear
model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps)
across the 8 segments for every subject. A subsequent, third-level analysis averaged contrast estimates over subjects.

@@

\todo[inline]{better speak of conditions than categories?}

% AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with annotated movie cuts \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
First, both annotations were split into eight parts corresponding to the eight
stimulus segments.

% AO events
All of the original 19 categories of descriptive nouns except \texttt{++} were
used as events. Some categories that were similar but offered only a small
amount of counts were pooled resulting in eleven new categories (see Table
\ref{tab:ao-events}). Events that fall into one of the two setting-related
category but also into another category were treated as belonging to
setting-related category (\texttt{se\_new} or \texttt{se\_old}).
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen for that segment.
\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
einem ihren Videos mal gesagt}
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after cuts, and to create contrasts of cross-modal negative control.
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) via Python script to
capture variance correlating with low-level perceptual processes.
% Reference to table
A short explanation and counts of the eleven speech-related event categories,
the five movie cut-related categories, and the two low-level confounds can be
found in Table \ref{tab:ao-events}.

@@

\caption{Overview of events to build the 18 regressors for the analysis of the
audio-only (AO) stimulus. Some of the original categories (female, females,
fname; male, males, mname; face, head; object, objects; see Table
\ref{tab:descr-nouns}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).

@@

For a description of the five control conditions for movie cuts see Table
\ref{tab:av-events}.}

@@

furn & moveable furniture insides \& outsides & \aoFurnAll & \aoFurnI & \aoFurnII & \aoFurnIII & \aoFurnIV & \aoFurnV & \aoFurnVI & \aoFurnVII & \aoFurnVIII \tabularnewline

@@

fg\_ad\_rms & root mean square (loudness) & \aoFgadrmsAll & \aoFgadrmsI & \aoFgadrmsII & \aoFgadrmsIII & \aoFgadrmsIV & \aoFgadrmsV & \aoFgadrmsVI & \aoFgadrmsVII & \aoFgadrmsVIII \tabularnewline

@@

% AV events
To create regressors for the AV analysis, we categorized the depicted location
in the frame following one of the 869 cuts into five categories
(cf. Table \ref{tab:av-events}): 1) a cut into an unfamiliar setting
(\texttt{vse\_new}), 2) familiar setting (\texttt{vse\_old}), 3) a switch of
locale within a setting (\texttt{vlo\_ch}), 4) a cut into an unfamiliar
perspective (\texttt{vpe\_new}), and 5) familiar perspective
(\texttt{vpe\_old}).
% null regressor
Here again, a null regressor was chosen for segment if it did not an event for
of a category.
% no cut condition: intro
A sixth regressors (\texttt{no\_cut}) serving a control condition and to created
to build negative control contrasts. Frames within movie shots lasting at least
\unit[20]{s} were pseudo-randomly chosen by the following rationale:
% how they were fitted
\texttt{no\_cut} event had to have a minimum distance of \unit[10]{s} to a movie
cut and to another \texttt{no\_cut} events.
% reference to table
A short explanation and counts of these six categories modeled as impulse
events, six additional event categories for low-level auditory and visual
features of the movie (here again continuous bins lasting \unit[40]{ms}), can be found in Table \ref{tab:av-events}.

\begin{table*}[t]
    \caption{Overview of events to build the 14 regressors for the analysis of the audio-only (AV) stimulus.
\texttt{fg\_av\_ger\_lr} (left-right difference in [+++???+++] of
consecutive movie frames).
\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames).
\texttt{fg\_av\_ger\_ud} (up-down difference in [+++???+++] of consecutive movie frames).
\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference) and \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For description of the two events categories of the audio-description's
narrator (\texttt{se\_new} and \texttt{se\_old}) to build contrast
of negative control see Table \ref{tab:ao-events}}
\label{tab:av-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
vse\_new &  change of the camera position to a setting not depicted before & \aoVsenewAll & \aoVsenewI & \aoVsenewII & \aoVsenewIII & \aoVsenewIV & \aoVsenewV & \aoVsenewVI & \aoVsenewVII & \aoVsenewVIII \tabularnewline
vse\_old & change of the camera position to a recurring setting & \aoVseoldAll & \aoVseoldI & \aoVseoldII & \aoVseoldIII & \aoVseoldIV & \aoVseoldV & \aoVseoldVI & \aoVseoldVII & \aoVseoldVIII \tabularnewline
vlo\_ch & change of the camera position to another locale within the same setting & \aoVlochAll & \aoVlochI & \aoVlochII & \aoVlochIII & \aoVlochIV & 0 & \aoVlochV & \aoVlochVI & \aoVlochVII \tabularnewline
vpe\_new & change of the camera position within a locale not depicted before & \aoVpenewAll & \aoVpenewI & \aoVpenewII & \aoVpenewIII & \aoVpenewIV & \aoVpenewV & \aoVpenewVI & \aoVpenewVII & \aoVpenewVIII \tabularnewline
% vpe_old has no events in 3. So the indices are shifted
vpe\_old & change of the camera position within a recurring locale & \aoVpeoldAll & \aoVpeoldI & \aoVpeoldII & 0 & \aoVpeoldIII & \aoVpeoldIV & \aoVpeoldV & \aoVpeoldVI & \aoVpeoldVII \tabularnewline
vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII \tabularnewline
se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII \tabularnewline
se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII \tabularnewline
fg\_av\_ger\_lr & XYZ & \avFgavgerlrAll & \avFgavgerlrI & \avFgavgerlrII & \avFgavgerlrIII & \avFgavgerlrIV & \avFgavgerlrV & \avFgavgerlrVI & \avFgavgerlrVII & \avFgavgerlrVIII \tabularnewline
fg\_av\_ger\_lrdiff & left-right volume difference & \avFgavgerlrdiffAll & \avFgavgerlrdiffI & \avFgavgerlrdiffII & \avFgavgerlrdiffIII & \avFgavgerlrdiffIV & \avFgavgerlrdiffV & \avFgavgerlrdiffVI & \avFgavgerlrdiffVII & \avFgavgerlrdiffVIII \tabularnewline
fg\_av\_ger\_ml & +++???+++ & \avFgavgermlAll & \avFgavgermlI & \avFgavgermlII & \avFgavgermlIII & \avFgavgermlIV & \avFgavgermlV & \avFgavgermlVI & \avFgavgermlVII & \avFgavgermlVIII \tabularnewline
fg\_av\_ger\_pd & +++???+++ & \avFgavgerpdAll & \avFgavgerpdI & \avFgavgerpdII & \avFgavgerpdIII & \avFgavgerpdIV & \avFgavgerpdV & \avFgavgerpdVI & \avFgavgerpdVII & \avFgavgerpdVIII \tabularnewline
fg\_av\_ger\_rms & root mean square (loudness) & \avFgavgerrmsAll & \avFgavgerrmsI & \avFgavgerrmsII & \avFgavgerrmsIII & \avFgavgerrmsIV & \avFgavgerrmsV & \avFgavgerrmsVI & \avFgavgerrmsVII & \avFgavgerrmsVIII \tabularnewline
fg\_av\_ger\_ud & +++???+++ & \avFgavgerudAll & \avFgavgerudI & \avFgavgerudII & \avFgavgerudIII & \avFgavgerudIV & \avFgavgerudV & \avFgavgerudVI & \avFgavgerudVII & \avFgavgerudVIII \tabularnewline
\end{tabular}
\end{table*}

% modeling of regressors from events
Events of both stimuli were convolved with a double gamma hemodynamic response
function (HRF).
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 13 regressors of the AO stimulus and
12 regressors of the AV stimulus across the time course of all stimulus segments
can be seen in Figure \ref{fig:reg-corr}.\todo{correct colors on horizontal
line; drop control regressors from figure}
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}). Regressors were created by convolving the events
        with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response
        function, temporally filtered with the same high-pass filter (cut-off
        \unit[150]{s}) as the BOLD time series, and concatenated across runs
    before computing the correlation.} \label{fig:reg-corr} \end{figure*}
